Manuscript title here

### 2025-11-17 manuscript.qmd
Producing Flowchart for participants

---
title: "Manuscript title here"
output: html_document
author: "Your name here"
bibliography: bibliography.bib
csl: vancouver.csl
---

@@

Abstract
========

@@

Background
----------

Methods
-------

Results
-------

Conclusion
----------

Introduction
============

<!-- Explain the scientific background and rationale for the
investigation being reported. End by stating the aim or specific
objectives, including any prespecified hypotheses. The introduction
should not be longer than 1-1.5 pages, typically 4-5 paragraphs, each
6-8 lines long. Support every statement with a citation -->....

Methods 
=======

Study design 
------------

@@

Setting
-------

@@

Participants
------------

@@

Variables and data sources/measurements
---------------------------------------

@@

Bias 
----

@@

Study size 
----------

@@

Quantitative variables
----------------------

@@

Statistical methods
-------------------

@@

Results
=======

@@

Participants
------------

(a) Report numbers of individuals at each stage of study—eg numbers
potentially eligible, examined for eligibility, confirmed eligible,
included in the study, completing follow-up, and analysed

(c) Consider use of a flow diagram

@@

Discussion
==========

@@

Conclusion
==========

@@

References
==========

>>>>

---
title: "Manuscript title here"
format: html
author: "Your name here"
bibliography: bibliography.bib
csl: vancouver.csl
---

@@

# Abstract

Hello

@@

## Background

## Methods

## Results

## Conclusion

# Introduction

<!-- Explain the scientific background and rationale for the
investigation being reported. End by stating the aim or specific
objectives, including any prespecified hypotheses. The introduction
should not be longer than 1-1.5 pages, typically 4-5 paragraphs, each
6-8 lines long. Support every statement with a citation -->

# Methods

## Study design

@@

## Setting

@@

## Participants

@@

## Variables and data sources/measurements

@@

## Bias

@@

## Study size

@@

## Quantitative variables

@@

## Statistical methods

@@

# Results

## Participants

<!-- (a) Report numbers of individuals at each stage of study—eg numbers
potentially eligible, examined for eligibility, confirmed eligible,
included in the study, completing follow-up, and analysed

(c) Consider use of a flow diagram -->

```{r flowchart, echo=FALSE}

library(DiagrammeR)
library(glue)
library(tidyverse)
library(gtsummary)
library(DiagrammeRsvg)
library(rsvg)         
source("main.R") ## This "imports" the main script file of your project and run any code in it

# Flowchart figure -----------------------------------------------------------

# ---- Counts for intermediate steps -----------------------------------------
n_excl_step1 <- n_total_merged_data - n_TBI_only_data
n_excl_step2 <- n_under18 + n_no_ofi

# ---- Labels ----------------------------------------------------------------
label_A <- glue(
  "Trauma registry 2012–2023\n",
  "n = {n_total_merged_data}"
)

label_B <- glue(
  "Identified TBI using AIS 1xxxxx.x\n",
  "n = {n_TBI_only_data}"
)

label_C <- glue(
  "Eligible adult TBI patients\n",
  "with OFI outcome\n",
  "n = {n_eligible}"
)

label_D <- glue(
  "Included (final analytic cohort)\n",
  "n = {n_final} adult TBI patients\n",
  "- OFI: {n_ofi} ({round(100 * n_ofi / n_final, 1)}%)\n",
  "- No OFI: {n_final - n_ofi}"
)

label_excl1 <- glue( 
  "Excluded (n = {n_excl_step1}):\n",
  "- No TBI according to AIS code"
  )

label_excl2 <- glue(
  "Excluded (n = {n_excl_step2}):\n",
  "- Age < 18 years: {n_under18}\n",
  "- No OFI outcome: {n_no_ofi}"
)

label_excl3 <- glue(
  "Excluded: missing data\n",
  "in covariates (n = {n_missing_cc})"
)

# ---- Producing the figure with exclusion boxes ------------------------------

g <- grViz(glue("
digraph TBI_flow {{

  graph [
    rankdir = TB,
    splines = ortho
  ]

  node [
    shape = box,
    style = rounded,
    fontname = 'Times New Roman',
    fontsize = 12,
    width = 3
  ]

  edge [
    arrowhead = normal
  ]

  // Main vertical line
  A [label = '{label_A}']
  B [label = '{label_B}']
  C [label = '{label_C}']
  D [label = '{label_D}']

  // Side exclusion boxes
  E1 [label = '{label_excl1}']
  E2 [label = '{label_excl2}']
  E3 [label = '{label_excl3}']

  // Invisible junction nodes on the vertical line
  J1 [shape=point, width=0.001, label=\"\", style=invis]
  J2 [shape=point, width=0.001, label=\"\", style=invis]
  J3 [shape=point, width=0.001, label=\"\", style=invis]

  // Main vertical line
  A -> J1 [arrowhead=none] 
  J1 -> B       
  B -> J2 [arrowhead=none] 
  J2 -> C 
  C -> J3 [arrowhead=none]
  J3 -> D

  // Branching arrows from the vertical line to exclusions
  J1 -> E1
  J2 -> E2
  J3 -> E3

  // Keep exclusions horizontally aligned with the junctions
  {{rank=same; J1; E1}}
  {{rank=same; J2; E2}}
  {{rank=same; J3; E3}}

}}
"))

# ---- Export (SVG + PNG) ----
svg_txt <- DiagrammeRsvg::export_svg(g)

dir.create("assets", showWarnings = FALSE)

out_svg <- file.path("assets", "flowchart.svg")
out_png <- file.path("assets", "flowchart.png")

cat(svg_txt, file = out_svg)
rsvg_png(out_svg, file = out_png, width = 1600, height = 2600)

knitr::include_graphics(out_png)

```

@@

@@

# Discussion

@@

# Conclusion

@@

# References
